Type Evolution in Interactive Programming Systems

### 2024-05-31 paper.tex
typo
Redefine \frameworkbox to use \leftbar

\DeclareRobustCommand{\frameworkbox}[2][gray!15]{
\begin{tcolorbox}[breakable,left=3pt,right=3pt,top=3pt,bottom=3pt,colback=#1,colframe=#1,parbox=false,
  width=\dimexpr\textwidth\relax,enlarge left by=0mm,boxsep=5pt,arc=0pt,enlarge top by=0.5em,%enlarge bottom by=0.0em,
  outer arc=0pt]\setlength{\parskip}{0.5em}#2
\end{tcolorbox}}
\newcommand{\frameworkboxtitle}[1]{\setlength{\parindent}{0em}{\firamedium #1.}\quad}

@@

\leftbar
\begin{wrapfigure}{r}{12em}
  \vspace{0em}
  \includegraphics[width=12em]{figures/arr-steps.png}
  \vspace{0em}
\end{wrapfigure}
\noindent\textbf{Primitive Type Transformations.}\quad
In this case study, the evolving type is the \texttt{State} type. When the type evolves,
the program logic (code) and the current live value of the type (data) needs to evolve
correspondingly. The challenge is easier if we see the evolution as a sequence of more primitive
transformations, such as those in Table~\ref{tbl:elmchanges}, that each has a corresponding
primitive code and data transformation. The primitive transformations may either be invoked
through a user interface, or inferred from textual code edits made by the programmer.

\endleftbar

\begin{comment}
\frameworkbox{
\begin{wrapfigure}{r}{12em}
\vspace{0em}
\includegraphics[width=12em]{figures/arr-steps.png}
\vspace{0em}
\end{wrapfigure}
\frameworkboxtitle{Primitive Type Transformations}
In this case study, the evolving type is the \texttt{State} type. When the type evolves,
the program logic (code) and the current live value of the type (data) needs to evolve
correspondingly. The challenge is easier if we see the evolution as a sequence of more primitive
transformations, such as those in Table~\ref{tbl:elmchanges}, that each has a corresponding
primitive code and data transformation. The primitive transformations may either be invoked
through a user interface, or inferred from textual code edits made by the programmer.
}
\end{comment}

@@

There has been estensive research on coordinating the evolution of interdependent layers of software, much of it guided by schema and types. But the vast majority of these techniques involve writing custom code in some specialized language, rather than through immediate action in an interactive programming system. Nevertheless it is important to understand these batch techniques to envision more interactive ones.

>>>>

\DeclareRobustCommand{\frameworkbox}[1]{\leftbar#1\endleftbar}
\newcommand{\frameworkboxtitle}[1]{\noindent{\firamedium #1.}\quad}

\begin{comment}
\DeclareRobustCommand{\frameworkbox}[2][gray!15]{
\begin{tcolorbox}[breakable,left=3pt,right=3pt,top=3pt,bottom=3pt,colback=#1,colframe=#1,parbox=false,
  width=\dimexpr\textwidth\relax,enlarge left by=0mm,boxsep=5pt,arc=0pt,enlarge top by=0.5em,%enlarge bottom by=0.0em,
  outer arc=0pt]\setlength{\parskip}{0.5em}#2
\end{tcolorbox}}
\newcommand{\frameworkboxtitle}[1]{\setlength{\parindent}{0em}{\firamedium #1.}\quad}
\end{comment}

@@

\frameworkbox{
\begin{wrapfigure}{r}{12em}
\vspace{0em}
\includegraphics[width=12em]{figures/arr-steps.png}
\vspace{0em}
\end{wrapfigure}
\frameworkboxtitle{Primitive Type Transformations}
In this case study, the evolving type is the \texttt{State} type. When the type evolves,
the program logic (code) and the current live value of the type (data) needs to evolve
correspondingly. The challenge is easier if we see the evolution as a sequence of more primitive
transformations, such as those in Table~\ref{tbl:elmchanges}, that each has a corresponding
primitive code and data transformation. The primitive transformations may either be invoked
through a user interface, or inferred from textual code edits made by the programmer.
}

@@

There has been extensive research on coordinating the evolution of interdependent layers of software, much of it guided by schema and types. But the vast majority of these techniques involve writing custom code in some specialized language, rather than through immediate action in an interactive programming system. Nevertheless it is important to understand these batch techniques to envision more interactive ones.
